Time invariant analysis of epidemics with \pkg{EpiCompare}

### 2021-01-12 jss/EpiCompare-paper/EpiCompare-paper.Rmd
minor update to paper with section 3 image

@@

In this section, we highlight a number of the functionalities available in \proglang{EpiCompare}.  These functionalities include data cleaning, visualization, simulation, and comparison, in accordance with the data analysis pipeline REF\ref{}. We show a full data analysis from beginning to end that can be accomplished in a streamlined and standardized manner.

@@

>>>>

\ben{**The goals of this section is to present parts of the data science pipeline, introduce how we help, why they are useful and the ideas behind it.**}

\begin{figure}[!ht]
    \centering
    \includegraphics[width = 1\textwidth]{images/pipeline2.png}
    \caption{How \pkg{EpiCompare} supplements and aids in the epidemiological data analysis pipeline.}
    \label{fig:pipeline2}
\end{figure}

@@

In this section, we highlight a number of the functionalities available in \pkg{EpiCompare}.  These functionalities include data cleaning, visualization, simulation, and comparison, in accordance with the data analysis pipeline \ref{fig:pipeline}. We show a full data analysis from beginning to end that can be accomplished in a streamlined and standardized manner.

@@

# Helpful Rmd tricks

### 2021-01-12 jss/EpiCompare-paper/EpiCompare-paper.tex
minor update to paper with section 3 image

Epidemics can be difficult to compare to one another due to differences
in diseases, locations, or population behaviors, or times. We focus on
comparisons between epidemics adjusting for time, both the relative unit
of rate of infection (e.g.~days, months, years) and the relative
beginning and end of an epidemic. By adjusting for the unit of infection
rate, we can focus on the ``lifetime'\,' of an epidemic, a view that is
concerned more with the total number of lives affected than due to a
time constraint. By adjusting for the relative beginning/end of an
infection we can compare, for example the first part of infection from
one city to another where this is some time gap in spread.

@@

@@

>>>>

Epidemics can be difficult to compare to one another due to differences
in diseases, locations, or population behaviors, or times. We focus on
comparisons between epidemics adjusting for time, both the relative unit
of rate of infection (e.g.~days, months, years) and the relative
beginning and end of an epidemic. By adjusting for the unit of infection
rate, we can focus on the ``lifetime'' of an epidemic, a view that is
concerned more with the total number of lives affected than due to a
time constraint. By adjusting for the relative beginning/end of an
infection we can compare, for example the first part of infection from
one city to another where this is some time gap in spread.

@@

\textcolor{violet}{**The goals of this section is to present parts of the data science pipeline, introduce how we help, why they are useful and the ideas behind it.**}

\begin{figure}[!ht]
    \centering
    \includegraphics[width = 1\textwidth]{images/pipeline2.png}
    \caption{How \pkg{EpiCompare} supplements and aids in the epidemiological data analysis pipeline.}
    \label{fig:pipeline2}
\end{figure}

@@

\hypertarget{helpful-rmd-tricks}{%
\section{Helpful Rmd tricks}\label{helpful-rmd-tricks}}
